Figures to insert in text

### 2018-03-10 Chapters/sdm-performance.tex
SDM Performance scan, read, write for Amazon EC2 instances

>>>>

\begin{table}[!htb]
\centering
\begin{tabular}{| l | r | r | r |}
    \hline
    & Loops & Scans / second & Scan time (ms) \\ \hline
    Linear scan & 1000 & 15.44 & 64.73 \\
    Thread scan & 5000 & 30.47 & 32.81 \\
    OpenCL scan & 5000 & 93.63 & 10.67 \\ \hline
    \hline
    & Loops & Ops / second & Op. time (ms) \\ \hline
    Thread write & 1000 & 23.44 & 42.64 \\
    Thread single read & 1000 & 28.26 & 35.37 \\
    OpenCL write & 1000 & 51.78 & 19.31 \\
    OpenCL single read & 1000 & 85.31 & 11.72 \\
    \hline
\end{tabular}
\caption{Amazon EC2 p2.xlarge with Intel Xeon E5-2686v4 processor, 61GB DDR3 RAM, and NVIDIA K80 GPU. Running an SDM with $n=1,000$ bits, $H=1,000,000$, and $r=451$.}
\end{table}

\begin{table}[!htb]
\centering
\begin{tabular}{| l | r | r | r |}
    \hline
    & Loops & Scans / second & Scan time (ms) \\ \hline
    Linear scan & 1000 & 52.35 & 19.09 \\
    Thread scan & 5000 & 100.48 & 9.95 \\
    OpenCL scan & 5000 & 145.18 & 6.88 \\ \hline
    \hline
    & Loops & Ops / second & Op. time (ms) \\ \hline
    Thread write & 2000 & 84.73 & 11.80 \\
    Thread single read & 2000 & 95.26 & 10.49 \\
    OpenCL write & 2000 & 113.01 & 8.84 \\
    OpenCL single read & 2000 & 133.19 & 7.50 \\
    \hline
\end{tabular}
\caption{Amazon EC2 p2.xlarge with Intel Xeon E5-2686v4 processor, 61GB DDR3 RAM, and NVIDIA K80 GPU. Running an SDM with $n=256$ bits, $H=1,000,000$, and $r=103$.}
\end{table}

\begin{table}[!htb]
\centering
\begin{tabular}{| l | r | r | r |}
    \hline
    & Loops & Scans / second & Scan time (ms) \\ \hline
    Linear scan & 100 & 1.66 & 600.75 \\
    Thread scan & 500 & 3.37 & 296.56 \\
    OpenCL scan & 1000 & 21.39 & 46.73 \\ \hline
    \hline
    & Loops & Ops / second & Op. time (ms) \\ \hline
    Thread write & 500 & 2.60 & 383.50 \\
    Thread single read & 500 & 3.24 & 307.97 \\
    OpenCL write & 1000 & 8.18 & 122.17 \\
    OpenCL single read & 55.47 & 18.02 & 55.47 \\
    \hline
\end{tabular}
\caption{EC p2.xlarge 10,000-bits}
\caption{Amazon EC2 p2.xlarge with Intel Xeon E5-2686v4 processor, 61GB DDR3 RAM, and NVIDIA K80 GPU. Running an SDM with $n=10,000$ bits, $H=1,000,000$, and $r=4845$.}
\end{table}

\begin{table}[!htb]
\centering
\begin{tabular}{| l | r | r | r |}
    \hline
    & Loops & Scans / second & Scan time (ms) \\ \hline
    Linear scan & 1000 & 17.13 & 58.34 \\
    Thread scan & 5000 & 60.98 & 16.39 \\
    OpenCL scan & 5000 & 1175.88 & 0.85 \\ \hline
    \hline
    & Loops & Ops / second & Op. time (ms) \\ \hline
    Thread write & 1000 & 35.12 & 28.47 \\
    Thread single read & 1000 & 57.31 & 17.44 \\
    OpenCL write & 1000 & 113.98 & 8.77 \\
    OpenCL single read & 1000 & 549.12 & 1.82 \\
    \hline
\end{tabular}
\caption{Amazon EC2 p3.2xlarge with Intel Xeon E5-2686v4 processor, 488GB DDR3 RAM, and NVIDIA Tesla V100 GPU. Running an SDM with $n=1,000$ bits, $H=1,000,000$, and $r=451$.}
\end{table}

\begin{table}[!htb]
\centering
\begin{tabular}{| l | r | r | r |}
    \hline
    & Loops & Scans / second & Scan time (ms) \\ \hline
    Linear scan & 1000 & 56.80 & 17.60 \\
    Thread scan & 5000 & 192.54 & 5.19 \\
    OpenCL scan & 5000 & 1565.28 & 0.63 \\ \hline
    \hline
    & Loops & Ops / second & Op. time (ms) \\ \hline
    Thread write & 2000 & 131.64 & 7.59 \\
    Thread single read & 2000 & 161.97 & 6.17 \\
    OpenCL write & 2000 & 427.38 & 2.33 \\
    OpenCL single read & 2000 & 987.95 & 1.01 \\
    \hline
\end{tabular}
\caption{Amazon EC2 p3.2xlarge with Intel Xeon E5-2686v4 processor, 488GB DDR3 RAM, and NVIDIA Tesla V100 GPU. Running an SDM with $n=256$ bits, $H=1,000,000$, and $r=103$.}
\end{table}

\begin{table}[!htb]
\centering
\begin{tabular}{| l | r | r | r |}
    \hline
    & Loops & Scans / second & Scan time (ms) \\ \hline
    Linear scan & 100 & 1.84 & 540.97 \\
    Thread scan & 500 & 5.03 & 198.74 \\
    OpenCL scan & 1000 & 174.05 & 5.74 \\ \hline
    \hline
    & Loops & Ops / second & Op. time (ms) \\ \hline
    Thread write & 500 & 4.50 & 222.08 \\
    Thread single read & 500 & 6.89 & 145.01 \\
    OpenCL write & 1000 & 12.42 & 80.48 \\
    OpenCL single read & 1000 & 71.46 & 13.99 \\
    \hline
\end{tabular}
\caption{Amazon EC2 p3.2xlarge with Intel Xeon E5-2686v4 processor, 488GB DDR3 RAM, and NVIDIA Tesla V100 GPU. Running an SDM with $n=10,000$ bits, $H=1,000,000$, and $r=4845$.}
\end{table}
